Distortion-corrected kernel density estimate on Riemannian manifolds

### 2022-07-23 paper/paper.Rmd
Sec 2 done

The Riemannian metric $g$ is a symmetric and positive definite tensor field which defines an inner product $\langle,\rangle_g$ on the tangent space $T_\pmb{p} M$ for every point $\pmb{p}\in M$. If the inner product of the tangent space is known for a given geometry, the Riemannian metric is a good measure to recover the geometry of the manifold. For each point $\pmb{p} \in M$ in any embedding coordinate system, the Riemannian metric $g$ is a $d\times d$ symmetric positive definite matrix, where $d$ is the dimension of the manifold.

The inner product between two vectors $u,v \in T_\pmb{p}M$, given by $\langle u,v \rangle_g=g_{ij}u^iv^j$[^1], can be used to define some geometric quantities, such as the vector norm $|u|=\sqrt{\langle u,u \rangle_g}$ and the angle between two vectors $\cos{\theta}=\frac{\langle u,v \rangle_g}{|u| |v|}$ in the tangent space.
[^1]: Here the Einstein notation is used where superscripts denote summation over $i$ and $j$.

>>>>

The Riemannian metric $g$ is a symmetric and positive definite tensor field which defines an inner product $\langle,\rangle_g$ on the tangent space $T_{\pmb{p}} M$ for every point $\pmb{p} \in M$. If the inner product of the tangent space is known for a given geometry, the Riemannian metric is a good measure to recover the geometry of the manifold. For each point $\pmb{p} \in M$ in any embedding coordinate system, the Riemannian metric $g$ is a $d\times d$ symmetric positive definite matrix, where $d$ is the dimension of the manifold.

The inner product between two vectors $u,v \in T_{\pmb{p}}M$, given by $\langle u,v \rangle_g=g_{ij}u^iv^j$[^1], can be used to define some geometric quantities, such as the vector norm $|u|=\sqrt{\langle u,u \rangle_g}$ and the angle between two vectors $\cos{\theta}=\frac{\langle u,v \rangle_g}{|u| |v|}$ in the tangent space.
[^1]: Here the Einstein notation is used where superscripts denote summation over $i$ and $j$.
